Models with year

### 2022-10-11 Rmd/model_with_year.Rmd
plot_models

\newpage
Predicte values of seed number
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p1=plot_model(mod_seed_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus",show.data = TRUE)
p2=plot_model(mod_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus",show.data = TRUE)
p3=plot_model(mod_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer",show.data = TRUE)
p4=plot_model(mod_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis",show.data = TRUE)
p5=plot_model(mod_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis",show.data = TRUE)
p6=plot_model(mod_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius",show.data = TRUE)

@@

p7=plot_model(mod_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum",show.data = TRUE)
p8=plot_model(mod_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium",show.data = TRUE)
p9=plot_model(mod_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata",show.data = TRUE)
p10=plot_model(mod_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas",show.data = TRUE)
p11=plot_model(mod_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus",show.data = TRUE)
p12=plot_model(mod_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans",show.data = TRUE)

@@

Predicted values of Seeds for *Cistus crispus*
```{r,echo=FALSE, warning=FALSE,message=FALSE}
get_model_data(mod_seed_year.1$mod[[2]], type = "int")

@@

@@

\newpage
Predicted values of Seeds
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

ggarrange(plot_model(mod_mix_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis", show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum", show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_mix_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
,ncol=3,nrow = 4)

@@

@@

Predicted values of Seeds 
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

ggarrange(plot_model(mod_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE), ncol=3,nrow = 4)

@@

@@

@@

ggarrange(plot_model(mod_mix_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_mix_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)

@@

Could not compute variance-covariance matrix of predictions. No confidence intervals are returned

@@

ggarrange(plot_model(mod_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)

@@

@@

@@

ggarrange(plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)

@@

@@

ggarrange(plot_model(mod_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
plot_model(mod_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)

@@

@@

@@

>>>>

\newpage
Predicte values of seed number

p1=plot_model(mod_seed_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
p2=plot_model(mod_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
p6=plot_model(mod_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

@@

p7=plot_model(mod_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

@@

Predicted values of Seeds for *Cistus crispus*

```{r,echo=FALSE, warning=FALSE,message=FALSE}
get_model_data(mod_seed_year.1$mod[[2]], type = "int")

@@

elimana algunos valores de interacciones en *C.monspeliensis*, *H.halimifolium* y *T.fructicans*: fixed-effect model matrix is rank deficient so dropping 3 columns / coefficients - 1 column / coefficient - 1 column / coefficient

Además boundary (singular) fit: see help('isSingular')

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

@@

\newpage
Predicted values of Seeds

p1=plot_model(mod_mix_seed_year.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
p2=plot_model(mod_mix_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_mix_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_mix_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_mix_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
p6=plot_model(mod_mix_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_mix_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
p2.1=plot_model(mod_mix_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
p3.1=plot_model(mod_mix_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
p4.1=plot_model(mod_mix_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis", show.data = TRUE)
p5.1=plot_model(mod_mix_seed_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
p6.1=plot_model(mod_mix_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)

@@

p7=plot_model(mod_mix_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_mix_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_mix_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_mix_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_mix_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_mix_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_mix_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum", show.data = TRUE)
p8.1=plot_model(mod_mix_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
p9.1=plot_model(mod_mix_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
p10.1=plot_model(mod_mix_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
p11.1=plot_model(mod_mix_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
p12.1=plot_model(mod_mix_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)

@@

Predicted values of Seeds

@@

p1=plot_model(mod_seed_year_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
p2=plot_model(mod_seed_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_seed_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_seed_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_seed_year_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
p6=plot_model(mod_seed_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
p2.1=plot_model(mod_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
p3.1=plot_model(mod_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
p4.1=plot_model(mod_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
p5.1=plot_model(mod_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
p6.1=plot_model(mod_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)

p7=plot_model(mod_seed_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_seed_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_seed_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_seed_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_seed_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_seed_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
p8.1=plot_model(mod_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
p9.1=plot_model(mod_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
p10.1=plot_model(mod_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
p11.1=plot_model(mod_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
p12.1=plot_model(mod_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)

@@

elimana algunos valores de interacciones en *Asphodelus fistulosus* - *Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans*: fixed-effect model matrix is rank deficient so dropping 3 columns / coefficients - 1 column / coefficient - 1 column / coefficient

Además boundary (singular) fit: see help('isSingular')

@@

Predicted values of Seeds

*Asphodelus fistulosus* - *Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans* 
Could not compute variance-covariance matrix of predictions. No confidence intervals are returned

p1=plot_model(mod_mix_seed_year_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
p2=plot_model(mod_mix_seed_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_mix_seed_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_mix_seed_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_mix_seed_year_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
p6=plot_model(mod_mix_seed_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_mix_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
p2.1=plot_model(mod_mix_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
p3.1=plot_model(mod_mix_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
p4.1=plot_model(mod_mix_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
p5.1=plot_model(mod_mix_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
p6.1=plot_model(mod_mix_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)

@@

p7=plot_model(mod_mix_seed_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_mix_seed_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_mix_seed_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_mix_seed_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_mix_seed_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_mix_seed_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_mix_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
p8.1=plot_model(mod_mix_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
p9.1=plot_model(mod_mix_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
p10.1=plot_model(mod_mix_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
p11.1=plot_model(mod_mix_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
p12.1=plot_model(mod_mix_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)

@@

Predicted values of Seeds

p1=plot_model(mod_seed_year_no_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
p2=plot_model(mod_seed_year_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_seed_year_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_seed_year_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_seed_year_no_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
p6=plot_model(mod_seed_year_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
p2.1=plot_model(mod_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
p3.1=plot_model(mod_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
p4.1=plot_model(mod_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
p5.1=plot_model(mod_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
p6.1=plot_model(mod_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)

@@

p7=plot_model(mod_seed_year_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_seed_year_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_seed_year_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_seed_year_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_seed_year_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_seed_year_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
p8.1=plot_model(mod_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
p9.1=plot_model(mod_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
p10.1=plot_model(mod_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
p11.1=plot_model(mod_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
p12.1=plot_model(mod_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)

@@

Warning messages:Some predictor variables are on very different scales: consider rescaling. The warning occurred in Salvia rosmarinus
No_Apis_visit_rate:Year2016 -> 364.706 (Estimate); 813.126 (std.error)

elimana algunos valores de interacciones en *C.monspeliensis*, *H.halimifolium* y *T.fructicans*: fixed-effect model matrix is rank deficient so dropping 3 columns / coefficients - 1 column / coefficient - 1 column / coefficient

@@

\newpage
Predicted values of Seeds

*C.monspeliensis*, *H.halimifolium* y *T.fructicans*
Could not compute variance-covariance matrix of predictions. No confidence intervals are returned
```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}

p1=plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
p2=plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
p6=plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = T)
p2.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = T)
p3.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = T)
p4.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = T)
p5.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = T)
p6.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = T)

p7=plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = T)
p8.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = T)
p9.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = T)
p10.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = T)
p11.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = T)
p12.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = T)

@@

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

@@

Predicted values of Seeds

*Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans* 
Warning message:
In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,:  prediction from a rank-deficient fit may be misleading

p1=plot_model(mod_seed_year_hym.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
p2=plot_model(mod_seed_year_hym.1$mod[[2]], type = "pred", title = " Cistus crispus")
p3=plot_model(mod_seed_year_hym.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
p4=plot_model(mod_seed_year_hym.1$mod[[4]], type = "pred",title = "Cistus libanotis")
p5=plot_model(mod_seed_year_hym.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
p6=plot_model(mod_seed_year_hym.1$mod[[6]], type = "pred",title = " Cistus salviifolius")

p1.1=plot_model(mod_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
p2.1=plot_model(mod_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
p3.1=plot_model(mod_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
p4.1=plot_model(mod_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
p5.1=plot_model(mod_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
p6.1=plot_model(mod_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)

p7=plot_model(mod_seed_year_hym.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_seed_year_hym.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_seed_year_hym.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_seed_year_hym.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_seed_year_hym.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_seed_year_hym.1$mod[[12]], type = "pred",title = " Teucrium fruticans")

p7.1=plot_model(mod_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
p8.1=plot_model(mod_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
p9.1=plot_model(mod_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
p10.1=plot_model(mod_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
p11.1=plot_model(mod_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
p12.1=plot_model(mod_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)

@@

**B-** linear mixed model with site ID like random factor
fixed-effect model matrix is rank deficient so dropping 1 column / coefficient de varia especies

@@

fixed-effect model matrix is rank deficient so dropping 1 column / coefficient

@@

p7=plot_model(mod_mix_seed_year_richness.1$mod[[7]], type = "pred",title = " Halimium calycinum")
p8=plot_model(mod_mix_seed_year_richness.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
p9=plot_model(mod_mix_seed_year_richness.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
p10=plot_model(mod_mix_seed_year_richness.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
p11=plot_model(mod_mix_seed_year_richness.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
p12=plot_model(mod_mix_seed_year_richness.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
